Dialect: A Compact Line Notation Based on SMILES

### 2022-06-19 manuscript.tex
Adds figure for node order. closes #116
Adds figure for node and edge associations. closes #117

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Node Order. Nodes in a molecular tree assume the order in which they were added through depth-first construction.}
    \label{fig:node-order}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Nodes and Edge Associations. Three node/edge associations are possible within a molecular tree. A parent atom can be connected to a child atom through a bond (left). A parent atom can also be connected to a child bridge node through a bond (center). Finally, an atom can be connected, without bonding, to a child atom through a gap (right).}
    \label{fig:nodes-and-edges}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=2.5cm]{node-order.pdf}
    \caption{Node Order. Nodes in a molecular tree assume the order in which they were added through depth-first construction. Parents precede children, and children added first preceded those added later.}
    \label{fig:node-order}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=4in]{node-and-edge-associations.pdf}
    \caption{Nodes and Edge Associations. Three node/edge associations are possible within a molecular tree. A parent atom can be connected to a child atom through a bond (left). A parent atom can also be connected to a child bridge node through a bond (center). Finally, an atom can be connected, without bonding, to a child atom through a gap (right).}
    \label{fig:nodes-and-edge-associations}
\end{figure}
